\section{References}

\noindent BBC. (2022) \textit{Timeline - History of the BBC} [online]. Available at \url{https://www.bbc.co.uk/historyofthebbc/bbc-100/timeline/} (accessed on 18th January 2024).
\vspace{0.2cm}

\noindent Pilnick, C. Baer, S, W. (1973) \textit{Cable television: A guide to the technology} [online]. Available at \url{https://www.rand.org/content/dam/rand/pubs/reports/2006/R1141.pdf} (accessed on 18th January 2024).
\vspace{0.2cm}

\noindent Ofcom. (2023) \textit{Media Nations report 2023} [online]. Available at \url{https://www.ofcom.org.uk/__data/assets/pdf_file/0029/265376/media-nations-report-2023.pdf} (accessed on 18th January 2024).
\vspace{0.2cm}

\noindent Ampere Analysis. (2023) \textit{Almost half of Internet users say they have switched off broadcast TV} [online]. Available at \url{https://www.ampereanalysis.com/press/release/dl/almost-half-of-internet-users-say-they-have-switched-off-broadcast-tv} (accessed on 18th January 2024).
\vspace{0.2cm}

\noindent Statista. (2023) \textit{Household penetration of smart TV sets in the United Kingdom (UK) from 2014 to 2023} [online]. Available at \url{https://www.statista.com/statistics/654074/smart-tv-penetration-in-uk-households/} (accessed on 18th January 2024).
\vspace{0.2cm}

\noindent Statista. (2022) \textit{Distribution of television platforms among households in the United Kingdom (UK) in 2022} [online]. Available at \url{https://www.statista.com/statistics/297494/top-uk-tv-platforms-among-households/} (accessed on 29th February 2024).
\vspace{0.2cm}

\noindent Amazon. (2021) \textit{Linear TV Integration Guide Overview} [online]. Available at \url{https://developer.amazon.com/docs/fire-tv/linear-tv-integration-guide-overview.html} (accessed on 18th January 2024).
\vspace{0.2cm}

\noindent Davie, T. (2022) \textit{A digital-first BBC} [online]. Available at \url{https://www.bbc.co.uk/mediacentre/speeches/2022/digital-first-bbc-director-general-tim-davie} (accessed on 18th January 2024).
\vspace{0.2cm}

\noindent Sparks, R. (2024) \textit{OKRs: the ultimate guide to objectives and key results} [online]. Available at \url{https://www.atlassian.com/agile/agile-at-scale/okr} (accessed on 18th January 2024).
\vspace{0.2cm}

\noindent Bowker O. (2023) \textit{Analysis of BBC process and proposal for a new API key management system}. Assignment for DC4000, MSc Digital and Technology Solutions Specialist, Aston University, Unpublished.
\vspace{0.2cm}

\noindent BBC Partnerships. (2023) \textit{Partnerships - one year on}. BBC. Unpublished.
\vspace{0.2cm}

\noindent Somerville, I. (2016) \textit{Software engineering}. Tenth edition, Global edition. London: Pearson Education.
\vspace{0.2cm}

\noindent Somerville, I. (2021) \textit{Engineering Software Products: An Introduction to Modern Software Engineering}. Global edition. London: Pearson Education.
\vspace{0.2cm}

\noindent Jasper, M. (2003) \textit{Beginning Reflective Practice}. Cheltenham: Nelson Thornes Ltd.
\vspace{0.2cm}

\noindent Amazon Web Services. (2024a) \textit{AWS Lambda} [online]. Available at \url{https://aws.amazon.com/lambda/} (accessed on 2nd February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024b) \textit{Amazon Simple Notification Service} [online]. Available at \url{https://aws.amazon.com/sns/} (accessed on 2nd February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024c) \textit{Amazon Simple Queue Service} [online]. Available at \url{https://aws.amazon.com/sqs/} (accessed on 2nd February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024d) \textit{Amazon S3} [online]. Available at \url{https://aws.amazon.com/s3/} (accessed on 2nd February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024e) \textit{Amazon DynamoDB} [online]. Available at \url{https://aws.amazon.com/dynamodb/} (accessed on 2nd February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024f) \textit{Amazon ElastiCache} [online]. Available at \url{https://aws.amazon.com/elasticache/} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024g) \textit{How AWS Pricing Works} [online]. Available at \url{https://docs.aws.amazon.com/pdfs/whitepapers/latest/how-aws-pricing-works/how-aws-pricing-works.pdf} (accessed on 20th February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024h) \textit{Optimistic locking with version number} [online]. Available at \url{https://docs.aws.amazon.com/amazondynamodb/latest/developerguide/DynamoDBMapper.OptimisticLocking.html} (accessed on 21st February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024i) \textit{Amazon EventBridge Pipes} [online]. Available at \url{https://aws.amazon.com/eventbridge/pipes/} (accessed on 20th February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024j) \textit{Amazon DynamoDB stream as a source} [online]. Available at \url{https://docs.aws.amazon.com/eventbridge/latest/userguide/eb-pipes-dynamodb.html} (accessed on 21st February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024k) \textit{PutMetricAlarm} [online]. Available at \url{https://docs.aws.amazon.com/AmazonCloudWatch/latest/APIReference/API_PutMetricAlarm.html#API_PutMetricAlarm_Errors} (accessed on 19th February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024l) \textit{UpdateEventSourceMapping} [online]. Available at \url{https://docs.aws.amazon.com/lambda/latest/api/API_UpdateEventSourceMapping.html} (accessed on 23rd February 2024).
\vspace{0.2cm}

\noindent Amazon Web Services. (2024m) \textit{Use Amazon CloudWatch metrics} [online]. Available at \url{https://docs.aws.amazon.com/AmazonCloudWatch/latest/monitoring/working_with_metrics.html} (accessed on 29th February 2024).
\vspace{0.2cm}

\noindent IBM. (2024) \textit{What is Redis?} [online]. Available at \url{https://www.ibm.com/topics/redis} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent IBM Cloud Education. (2021) \textit{SDK vs. API: What's the Difference?} [online]. Available at \url{https://www.ibm.com/blog/sdk-vs-api/} (accessed on 21st February 2024).
\vspace{0.2cm}

\noindent Redis Ltd. (2024a) \textit{Redis FAQ} [online]. Available at \url{https://redis.io/docs/get-started/faq/} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Redis Ltd. (2024b) \textit{Redis pipelining} [online]. Available at \url{https://redis.io/docs/manual/pipelining/} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Redis Ltd. (2024c) \textit{Transactions} [online]. Available at \url{https://redis.io/docs/interact/transactions/} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Redis Ltd. (2024d) \textit{Redis modules and blocking commands} [online]. Available at \url{https://redis.io/docs/reference/modules/modules-blocking-ops/} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Oracle Corporation. (2010) \textit{Defining Multithreading Terms} [online]. Available at \url{https://docs.oracle.com/cd/E19455-01/806-5257/6je9h032b/index.html} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Eyng, R. (2019) \textit{Redis: Pipelining, Transactions and Lua Scripts} [online]. Available at \url{https://rafaeleyng.github.io/redis-pipelining-transactions-and-lua-scripts} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Visual Paradigm. (2024) \textit{What is Spike in Scrum?} [online]. Available at \url{https://www.visual-paradigm.com/scrum/what-is-scrum-spike/} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Ugarte, A. (2024) \textit{What Is Thread-Safety and How to Achieve It?} [online]. Available at \url{https://www.baeldung.com/java-thread-safety} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Graefe, G. (2016) \textit{Revisiting optimistic and pessimistic concurrency control} [online]. Available at \url{https://www.labs.hpe.com/techreports/2016/HPE-2016-47.pdf} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Thornton, G. (2001) \textit{Optimistic Locking with Concurrency in Oracle} [online]. Available at \url{https://www.orafaq.com/papers/locking.pdf} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Weston, T. (2011) \textit{Optimistic and Pessimistic Concurrency Control with Shared Memory Models} [online]. Available at \url{https://baddotrobot.com/resources/concurrency-control-1.0-draft.pdf} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Apache Software Corporation. (2013) \textit{Deadlocks} [online]. Available at \url{https://db.apache.org/derby/docs/10.0/manuals/develop/develop75.html} (accessed on 9th February 2024).
\vspace{0.2cm}

\noindent Heil, C. (2022) \textit{Is Kanban the better Agile Approach in a Highly-Regulated Environment?} [online]. Available at \url{https://www2.deloitte.com/content/dam/Deloitte/de/Documents/risk/Deloitte_Agile_Approach_in_Highly_Regulated_Environments.pdf} (accessed on 12th February 2024).
\vspace{0.2cm}

\noindent Rehkopf, M. (2024) \textit{Kanban vs. scrum: which agile are you?} [online]. Available at \url{https://www.atlassian.com/agile/kanban/kanban-vs-scrum} (accessed on 12th February 2024).
\vspace{0.2cm}

\noindent Mauvius Group Inc. (2021) \textit{The official guide to the kanban method} [online]. Available at \url{https://resources.kanban.university/wp-content/uploads/2021/06/The-Official-Kanban-Guide_A4.pdf} (accessed on 12th February 2024).
\vspace{0.2cm}

\noindent Jenkins. (2024) \textit{Pipeline Syntax} [online]. Available at \url{https://www.jenkins.io/doc/book/pipeline/syntax/} (accessed on 12th February 2024).
\vspace{0.2cm}

\noindent Rodriguez, P. Haghighatkhah, A. Lwakatare, L, E. Teppola, S. Suomalainen, T. Eskeli, J. Karvonen, T. Kuvaja, P. Verner, J, M. Oivo, M. (2017) 'Continuous Deployment of Software Intensive Products and Services: A Systematic Mapping Study', Journal of Systems and Software, Vol. 123, pp. 263-291. Available at: \url{https://doi.org/10.1016/j.jss.2015.12.015}
\vspace{0.2cm}

\noindent Taibi, D. Janes, A. Lenarduzzi, V. (2017) 'How developers perceive smells in source code: A replicated study', Information and Software Technology, Vol. 92, pp. 223-235. Available at: \url{https://doi.org/10.1016/j.infsof.2017.08.008}
\vspace{0.2cm}

\noindent Xu, L. Guo, T. Dou, W. Wang, W. Wei, J. (2019) 'An experimental evaluation of garbage collectors on big data applications', Proceedings of the VLDB Endowment, Volume 12, Issue 5, pp 570-583. Available at: \url{https://doi.org/10.14778/3303753.3303762}
\vspace{0.2cm}

\noindent Olbrich, S. Cruzes, S, D. Basili, V. Zazworka, N. (2009) 'The evolution and impact of code smells: A case study of two open source systems', 2009 3rd International Symposium on Empirical Software Engineering and Measurement. Available at: \url{https://doi.org/10.1109/ESEM.2009.5314231}
\vspace{0.2cm}

\noindent Mateus, L. Andre, H. (2022) 'How and why we end up with complex methods: a multi-language study', Empirical Software Engineering, Vol. 27, Issue 5, Article Number 115. Available at: \url{https://doi.org/10.1007/s10664-022-10144-3}
\vspace{0.2cm}

\noindent Avelino, G. Passos, L. Hora, A. Valente, T, M. (2016) 'A novel approach for estimating Truck Factors', 2016 IEEE 24th International Conference on Program Comprehension (ICPC). Available at: \url{https://doi.org/10.1109/ICPC.2016.7503718}
\vspace{0.2cm}

\noindent Department of Defence. (2021) \textit{DoD Enterprise DevSecOps Fundamentals} [online]. Available at \url{https://dodcio.defense.gov/Portals/0/Documents/Library/DoDEnterpriseDevSecOpsFundamentals.pdf} (accessed on 14th February 2024).
\vspace{0.2cm}

\noindent NSA. (2023) \textit{Defending Continuous Integration/Continuous Delivery (CI/CD) Environments} [online]. Available at \url{https://media.defense.gov/2023/Jun/28/2003249466/-1/-1/0/CSI_DEFENDING_CI_CD_ENVIRONMENTS.PDF} (accessed on 14th February 2024).
\vspace{0.2cm}

\noindent OWASP Foundation. (2023) \textit{OWASP Top 10 CI/CD Security Risks} [online]. Available at \url{https://owasp.org/www-project-top-10-ci-cd-security-risks/} (accessed on 14th February 2024).
\vspace{0.2cm}

\noindent Wikström, A. (2019) \textit{Benefits and challenges of Continuous Integration and Delivery - A Case Study} [online]. Available at \url{https://core.ac.uk/download/pdf/226768285.pdf} (accessed on 14th February 2024).
\vspace{0.2cm}

\noindent Fairbanks, J. Tharigonda, A. Eisty, N, U. (2023) \textit{Analyzing the Effects of CI/CD on Open Source Repositories in GitHub and GitLab} [online]. Available at \url{https://arxiv.org/pdf/2303.16393.pdf} (accessed on 14th February 2024).
\vspace{0.2cm}

\noindent GoRetro. (2023) \textit{Ways of Working} [online]. Available at \url{https://www.goretro.ai/glossary/ways-of-working} (accessed on 14th February 2024).
\vspace{0.2cm}

\noindent Banerjee, A. (2017) 'System Changeover Policy and Precautions', International Journal of Advanced Engineering and Management, Vol. 2, No. 9, pp. 214-218. Available at: \url{https://doi.org/10.24999/IJOAEM/02090048}
\vspace{0.2cm}

\noindent Smyth, D. (2020) \textit{Changeover Techniques} [online]. Available at \url{https://smallbusiness.chron.com/changeover-techniques-34890.html} (accessed on 15th February 2024).
\vspace{0.2cm}

\noindent IoRedis. (2024) \textit{README - ioredis} [online]. Available at \url{https://ioredis.readthedocs.io/en/stable/README/#transparent-key-prefixing} (accessed on 15th February 2024).
\vspace{0.2cm}

\noindent Rustagi, V. (2023) \textit{Strategies To Run Old \& new Systems Simultaneously Using The Same Database} [online]. Available at \url{https://metaorangedigital.com/blog/strategies-to-run-old-new-systems-simultaneously-using-the-same-database/} (accessed on 15th February 2024).
\vspace{0.2cm}

\noindent Bigelow, J, S. (2020) \textit{What are the types of requirements in software engineering?} [online]. Available at \url{https://www.techtarget.com/searchsoftwarequality/answer/What-are-requirements-types} (accessed on 16th February 2024).
\vspace{0.2cm}

\noindent Karolis, N, Saulius, G. (2023) 'Causal Knowledge Modelling for Agile Development of Enterprise Application Systems', Informatica (Netherlands), Vol. 34 Issue 1, p 124. Available at: \url{https://doi.org/10.15388/23-INFOR510}
\vspace{0.2cm}

\noindent Eduardo, M. (2022) 'Moscow Rules: A Quantitative Exposé', Lecture Notes in Business Information Processing, Vol. 445, pp 19-34. Available at: \url{https://doi.org/10.1007/978-3-031-08169-9_2}
\vspace{0.2cm}

\noindent Kim, M. Park, S. Sugumaran, V. Yang, H. (2007) 'Managing requirements conflicts in software product lines: A goal and scenario based approach', Data \& Knowledge Engineering, Vol. 61 Issue 3, pp 417-432. Available at: \url{https://doi.org/10.1016/j.datak.2006.06.009}
\vspace{0.2cm}

\noindent Kanungo, S, Morena, D, R. (2023) 'Concurrency versus consistency in NoSQL databases', Journal of Autonomous Intelligence, Vol. 7 Issue 3. Available at: \url{https://doi.org/10.32629/jai.v7i3.936}
\vspace{0.2cm}

\noindent Sanders, R. (1987), 'THE PARETO PRINCIPLE: ITS USE AND ABUSE', Journal of Services Marketing, Vol. 1 No. 2, pp. 37-40. Available at: \url{https://doi.org/10.1108/eb024706}
\vspace{0.2cm}

\noindent Hashimi, A, L. Gravell, A. (2020), 'Spikes in Agile Software Development: An Empirical Study', 2020 International Conference on Computational Science and Computational Intelligence (CSCI). Available at: \url{https://doi.org/10.1109/CSCI51800.2020.00319}
\vspace{0.2cm}

\noindent Hashimi, A, L. Abduldaem, A. Gravell, A. (2022), 'Common Spikes Success Factors: An Industrial Investigation within Agile Software Development', 2022 12th International Conference on Software Technology and Engineering (ICSTE). Available at: \url{https://doi.org/10.1109/ICSTE57415.2022.00008}
\vspace{0.2cm}

\noindent Hashimi, A, L. Gravell, A. (2019) 'A Critical Review of the Use of Spikes in Agile Software Development', The Fourteenth International Conference on Software Engineering Advances. Available at: \url{https://www.researchgate.net/publication/340446921_A_Critical_Review_of_the_Use_of_Spikes_in_Agile_Software_Development}
\vspace{0.2cm}

\noindent Spinellis, D. (2019) 'State-of-the-Art Software Testing', IEEE Software, Vol. 34, Issue 5, pp 4-6. Available at: \url{https://doi.org/10.1109/MS.2017.3571564}
\vspace{0.2cm}

\noindent Kruchten, P. Nord, L, R. Ozkaya, I. Visser, J. (2012) 'Technical Debt in Software Development: from Metaphor to Theory Report on the Third International Workshop on Managing Technical Debt', ACM SIGSOFT Software Engineering Notes Advances, Vol. 37, No. 5, p. 36. Available at: \url{https://doi.org/10.1145/2347696.2347698}
\vspace{0.2cm}

\noindent Sathre, J, Zambreno, J. (2008) 'Automated software attack recovery using rollback and huddle', Des Autom Embed Syst, Vol. 12, pp. 243-260. Available at: \url{https://doi.org/10.1007/s10617-008-9020-4}
\vspace{0.2cm}

\noindent Leotta, M. García, B. Ricca, F. Whitehead, J. (2023) 'Challenges of End-to-End Testing with Selenium WebDriver and How to Face Them: A Survey', 2023 IEEE Conference on Software Testing, Verification and Validation (ICST). Available at: \url{https://doi.org/10.1109/ICST57152.2023.00039}
\vspace{0.2cm}

\noindent Zheng, J. (2021) 'Research on software development and test environment automation based on association rules', 2021 IEEE International Conference on Emergency Science and Information Technology (ICESIT). Available at: \url{https://doi.org/10.1109/ICESIT53460.2021.9696910}
\vspace{0.2cm}

\noindent Burghate, N. (2018) 'Work Breakdown Structure: Simplifying Project Management', International Journal of Commerce and Management Studies (IJCAMS), Vol. 3, No. 2. Available at: \url{https://www.ijcams.com/wp-content/uploads/2018/06/WBS.pdf}
\vspace{0.2cm}

\noindent Contan, A. Dehelean, C. Miclea, L. (2018) 'Test automation pyramid from theory to practice', 2018 IEEE International Conference on Automation, Quality and Testing, Robotics (AQTR). Available at: \url{https://doi.org/10.1109/AQTR.2018.8402699}
\vspace{0.2cm}

\noindent Glas, T. Hedén, F. (2021) \textit{Managing Technical Debt in XP Teams} [online]. Available at \url{https://fileadmin.cs.lth.se/cs/Education/EDAN80/Reports/2021/GlasHeden.pdf} (accessed on 19th February 2024).
\vspace{0.2cm}

\noindent Microsoft. (2021) \textit{Technical Spike} [online]. Available at \url{https://microsoft.github.io/code-with-engineering-playbook/design/design-reviews/recipes/technical-spike/} (accessed on 19th February 2024).
\vspace{0.2cm}

\noindent Microsoft. (2023) \textit{Fundamentals of garbage collection} [online]. Available at \url{https://learn.microsoft.com/en-us/dotnet/standard/garbage-collection/fundamentals} (accessed on 23rd February 2024).
\vspace{0.2cm}

\noindent Martins, J. (2023) \textit{7 common causes of scope creep, and how to avoid them} [online]. Available at \url{https://asana.com/resources/what-is-scope-creep} (accessed on 19th February 2024).
\vspace{0.2cm}

\noindent Raeburn, A. (2024) \textit{The work breakdown structure (WBS) for project management: What it is and how to use it} [online]. Available at \url{https://asana.com/resources/work-breakdown-structure} (accessed on 19th February 2024).
\vspace{0.2cm}

\noindent The Open Group. (2016) \textit{Implementation and Migration Elements} [online]. Available at \url{https://pubs.opengroup.org/architecture/archimate30-doc/chap13.html#_Toc451758082} (accessed on 19th February 2024).
\vspace{0.2cm}

\noindent Jonkers, H. Proper, E. Lankhorst, M, M. Quartel, A, C, D. Iacob, M. (2011) 'ArchiMate(R) for Integrated Modelling Throughout the Architecture Development and Implementation Cycle', 2011 IEEE 13th Conference on Commerce and Enterprise Computing. Available at: \url{https://doi.org/10.1109/CEC.2011.52}
\vspace{0.2cm}

\noindent Fakhoury, R. Braginsky, A. Keidar, I. Zuriel, Y. (2024) 'Nova: Safe Off-Heap Memory Allocation and Reclamation', Leibniz International Proceedings in Informatics, Volume 286, Article number 15. Available at: \url{https://doi.org/10.4230/LIPIcs.OPODIS.2023.15}
\vspace{0.2cm}

\noindent Silveria, A. (2020) \textit{GraphQL Live Querying with DynamoDB} [online]. Available at \url{https://arxiv.org/pdf/2008.00129.pdf} (accessed on 21st February 2024).
\vspace{0.2cm}

\noindent Wiggins, A. (2017) \textit{The Twelve-Factor App} [online]. Available at \url{https://12factor.net/} (accessed on 23rd February 2024).
\vspace{0.2cm}

\noindent Microsoft Azure. (2018) \textit{Understanding serverless cold start} [online]. Available at \url{https://azure.microsoft.com/en-us/blog/understanding-serverless-cold-start/} (accessed on 23rd February 2024).
\vspace{0.2cm}

\noindent Charles, Z. (2021) \textit{How to Enable/Disable a Lambda Trigger on a Schedule} [online]. Available at \url{https://zaccharles.medium.com/how-to-enable-disable-a-lambda-trigger-on-a-schedule-628f9925c853} (accessed on 23rd February 2024).
\vspace{0.2cm}

\noindent Matam, S. (2023) \textit{The History of Garbage Collection} [online]. Available at \url{https://www.linkedin.com/pulse/history-garbage-collection-sai-matam} (accessed on 23rd February 2024).
\vspace{0.2cm}

\noindent Wacker, M. (2015) \textit{Just Say No to More End-to-End Tests} [online]. Available at \url{https://testing.googleblog.com/2015/04/just-say-no-to-more-end-to-end-tests.html} (accessed on 26th February 2024).
\vspace{0.2cm}

\noindent Daly, N. (2022) \textit{What Is a Use Case?} [online]. Available at \url{https://www.wrike.com/blog/what-is-a-use-case/} (accessed on 26th February 2024).
\vspace{0.2cm}

\noindent Testim. (2021) \textit{End-to-End Testing vs Integration Testing} [online]. Available at \url{https://www.testim.io/blog/end-to-end-testing-vs-integration-testing/} (accessed on 26th February 2024).
\vspace{0.2cm}

\noindent Yang, L. (no date) \textit{Factors to Consider When Implementing Automated Software Testing} [online]. Available at \url{https://apps.dtic.mil/sti/tr/pdf/AD1022569.pdf} (accessed on 26th February 2024).
\vspace{0.2cm}

\noindent Talend Inc. (2024) \textit{ETL testing: A comprehensive guide to ensuring data quality and integration} [online]. Available at \url{https://www.talend.com/resources/etl-testing/} (accessed on 26th February 2024).
\vspace{0.2cm}

\noindent Grafana Labs. (2024) \textit{Grafana: The open observability platform | Grafana Labs} [online]. Available at \url{https://grafana.com/} (accessed on 27th February 2024).
\vspace{0.2cm}

\noindent Smith, S. (2023) \textit{Architect Modern Web Applications with ASP.NET Core and Azure} [online]. Available at \url{https://raw.githubusercontent.com/dotnet-architecture/eBooks/main/current/architecting-modern-web-apps-azure/Architecting-Modern-Web-Applications-with-ASP.NET-Core-and-Azure.pdf} (accessed on 26th February 2024).
\vspace{0.2cm}

\noindent Robinson, A. (2018) \textit{Want to Boost Your Bottom Line? Encourage Your Employees to Work on Side Projects} [online]. Available at \url{https://www.inc.com/adam-robinson/google-employees-dedicate-20-percent-of-their-time-to-side-projects-heres-how-it-works.html} (accessed on 4th March 2024).
\vspace{0.2cm}

\noindent Lloyd, K. (2023) \textit{iPlayer Schedules - BBC Partner Schedule Generator - Delta Update Technical Design}. BBC. Unpublished.
\vspace{0.2cm}

\newpage
