\section{Executive Summary}

\subsubsection*{Problem Statement}
SpaceChimp is a team in the BBC Partnerships group that is responsible for providing schedules data for live programming for all BBC channels to 
external partners. This system was designed to replace an external dependency the BBC had with a data provider. There is currently a system set up 
that statically generates this data every 15 minutes. This can leave to outdated User Interfaces (UIs) for partners as the data can be up to 15 minutes 
out of date, therefore displaying and linking users across the UK to the wrong or unavailable content.

\subsubsection*{Proposed Solution}
The current static system is to be updated to handle delta notifications that enable the updating and deleting of individual schedules instead of a 
refresh of all schedules every 15 minutes. To achieve this upgrade multiple steps must be taken:

\begin{itemize}
  \item An initial design will be created with architecture and algorithm, this design can then be implemented in a software spike to discover 
  problems and solutions.
  \item The work done in the spike will drive the design of the real product. This will be broken down into tasks and feature sets that developers 
  within the team will work on. Research will be done as part of this spike to find alternate routes where needed and will be presented in a spike 
  document.
  \item These tasks will go through the standard procedures of an enterprise team, development, testing and releasing. This development will include 
  handling of delta notifications, a garbage collector and integration and comparison tests to help gain confidence in the new system.
  \item Strategies to release the code into a live environment, used by 10s of millions of peoples, will be discussed and a release strategy for partners 
  will be decided upon.
\end{itemize}

\subsubsection*{Value}
This new system will allow the teams schedule offering to be as up to date as possible. When a partner requests the current data for a schedule to display in 
their UI, they will get the most up to date information possible. This work will also open the possibility to send update notifications directly to partners
so they no longer rely on requesting data at intervals and can request only the data that has been updated since their last call.

\subsubsection*{Final Thoughts and Next Steps}
This new system will lower overall processing time and cost due to schedules only be updated and deleted when needed. It will help partners offer more up to 
date UIs for their customers, help the BBC reach more people and reduce some overhead from external data providers. There is scope to extend this project 
further in the future to include notifications directly to partners as well as research and designs into how the new single-threaded system could one day 
be parallelised.

\vspace{0.2cm}
\noindent This report and its contents can be found in the following GitHub repo: \href{https://github.com/OMBowkerBBC/DC4400-Report}{\textbf{DC4400-Report}}.

\newpage
